Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-06-11 paper/paper.tex
added a few lines about kdown.

>>>>

The algorithm as described by Hoffmann, McCreesh, and Reilly \cite{DBLP:conf/aaai/HoffmannMR17} approaches the subgraph isomorphism problem by asking the question ``if a pattern graph cannot be found in the target, how much of the pattern graph can be found?''. The $k{\downarrow}$ algorithm tries to solve the subgraph isomorphism problem first for $k=0$ (the whole pattern graph can be found in the target), should that be not satisfiable, it tries to solve the problem for $k=1$ (one vertex cannot be matched) should that also not be satisfiable, it iterates $k$ further by a small number to keep the shrinking pattern graph within a reasonable size. By unmatching some vertices  invariants are weakened but kept effective. Specifically, invariants based around paths and degrees of vertices hold.

This technique bridges the subgraph isomorphism problem with the maximal common subgraph problem. The iteration of the decision problem (iterating over $k$) leads to an algorithm with rivalling runtimes.
